---
title: "Nova Scotia Wastewater COVID-19 dashboard (public version)"
description: |
  A dashboard I established to illustrates the SARS-CoV-2 viral RNA signal in wastewater collected from four wastewater treatment facilities (Halifax, Dartmouth, Mill Cove, and Eastern Passage) in Nova Scotia's central zone.
author:
  - name: Bofu Li
    url: {}
date: 2022-04-12
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I am glad that the Nova Scotia wastewater COVID-19 dashboard finally go public. This is a brief version which only show the cumulative viral loading from four wastewater treatment plants in Halifax. Hopefully, I can open another dashboard (research version) in the near future.  

For attribution, please cite this dashboard as:

Li, B.; Pickard, R.; Hayes, E.K.; Sweeney, C.L.; Erjavec, G.B.; Stoddart, A.K. and Gagnon, G.A. Nova Scotia COVID-19 Wastewater Surveillance - Centre for Water Resources Studies, Dalhousie University. 2022. https://cwrs.shinyapps.io/public_dashboard/.

<br>

```{r, echo= FALSE, layout="l-page", fig.cap = "Link to the dashboard (full screen): https://cwrs.shinyapps.io/public_dashboard/" }
knitr::include_app(" https://cwrs.shinyapps.io/public_dashboard/",
  height = "600px")
```



