---
title: "Lead (Pb) equilibrium solubility prediction and visualization"
description: |
   Lead (Pb) equilibrium solubility prediction and visualization.
author:
  - name: Bofu Li
    url: {}
date: 01-25-2022
output:
  distill::distill_article:
    self_contained: false
---

Our team published a data-driven review paper in the journal of ES&T to discuss about the research gap in the use of silicate-based corrosion inhibitor in lead (Pb) release control in drinking water distribution system [(Li et al. 2022)](https://pubs.acs.org/doi/abs/10.1021/acs.estlett.1c00671). In this work, calculate the equilibirum lead solubility model by using the package of [pbcusol](https://github.com/bentrueman/pbcusol) and [PHREEQC]( http://pubs.usgs.gov/tm/06/a43) developed by USGS.

We set the variables of pH, dic (dissolved organic carbon) and mineral phases (e.g., Cerussite, Hydcerussite, PbSiO3, Hxypyromorphite) [(Li et al. 2022)](https://pubs.acs.org/doi/abs/10.1021/acs.estlett.1c00671):

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r code, echo=TRUE}
library("tidyverse")
library("furrr") 
library("pbcusol")

possibly_sol <- possibly(
  eq_sol_fixed,
  otherwise = tibble(pb_ppb = NA_real_, phase = NA_real_)
)

future::plan("multisession")

model_output_data<- crossing(
  ph = seq(5, 12, by = 0.5), 
  dic = c(6, 120),
  phase = c("Hydcerussite", 
            "Cerussite",
            "Hxypyromorphite")
) %>% 
  mutate(po_4 = if_else(phase == "Hxypyromorphite", 1, 0)) %>% 
  rowid_to_column() %>% 
  group_by(rowid) %>% 
  nest() %>% 
  ungroup() %>% 
  mutate(
    output = furrr::future_map(
      data, 
      ~ possibly_sol(
        ph = .x$ph, dic = .x$dic, phosphate = .x$po_4,
        phase = .x$phase, buffer = "HCl",
        Na = .5, Cl = .5,
        element = "Pb"
      ) %>% 
        select(-phase)
    )
  ) %>%unnest(c(data, output))
```

Visualize the data using ggplot2. 

```{r vis,echo=TRUE}
library("PNWColors")
pal=pnw_palette("Sailboat",4, type = "discrete")
lab_1<-expression(bold("PbCO"[3]))
lab_2<-expression(bold("Pb"[5]*"(PO"[4]*")"[3]*"OH"))
lab_3<-expression(bold("Pb"[3]*"(CO"[3]*")"[2]*"(OH)"[2]))
lab_4<-expression (bold("PbSiO"[3]))

theme_set(
  theme_bw() +
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(fill=NA, colour = "black", size=1),
    axis.line = element_line(colour = "black",size=1),
    axis.text.x=element_text(colour="black",size=11,face="bold"),
    axis.text.y=element_text(colour="black",size=11,face="bold"),
    axis.title=element_text(size=11,colour="black",face="bold"),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.direction = "vertical",
    legend.background=element_blank(),
    legend.text = element_text(size=8.5,colour="black",face="bold"),
    legend.key.size =  unit(1, "cm"),
    legend.spacing.x = unit(0.1, 'cm'),
    legend.text.align = 0,
    legend.key.height = unit(.3, "cm")
  )
)

plot<- model_output_data%>% 
  ggplot(aes(pH, pb_ppb, col = phase, linetype = factor(dic))) + 
  geom_line(size = 1) + 
  scale_linetype(labels = function(breaks) paste0(breaks, "mg C/L")) +
  scale_y_log10(
    labels = function(breaks) 1e-3 * breaks,
    minor_breaks = unlist(map(1:6, ~ 1:9 * 10 ^ .x))
  ) +
  scale_colour_manual(
    breaks = c("Cerussite","Hxypyromorphite","Hydcerussite","PbSiO3"),
    values = pal,
    labels = c(lab_1, lab_2, lab_3, lab_4)
  ) +
  scale_shape(
    labels = c(
      expression(bold("background SiO"[2])), 
      expression(bold("added SiO"[2]))
    )
  ) +
  ylab("[Pb] (mg/L)") + 
  theme(
    legend.box.margin = margin(r = 20), 
    legend.spacing.x = unit(0, "cm"),
    legend.text = element_text(size = 6)
  )
```

```{r fig,fig.height=5, fig.width=5,preview=TRUE}
library("tidyverse")
model_output_data%>% 
  ggplot(aes(pH, pb_ppb, col = phase, linetype = factor(dic))) + 
  geom_line(size = 1) + 
  scale_linetype(labels = function(breaks) paste0(breaks, "mg C/L")) +
  scale_y_log10(
    labels = function(breaks) 1e-3 * breaks,
    minor_breaks = unlist(map(1:6, ~ 1:9 * 10 ^ .x))
  ) +
  scale_colour_manual(
    breaks = c("Cerussite","Hxypyromorphite","Hydcerussite","PbSiO3"),
    values = pal,
    labels = c(lab_1, lab_2, lab_3, lab_4)
  ) +
  scale_shape(
    labels = c(
      expression(bold("background SiO"[2])), 
      expression(bold("added SiO"[2]))
    )
  ) +
  ylab("[Pb] (mg/L)") + 
  theme(
    legend.box.margin = margin(r = 20), 
    legend.spacing.x = unit(0, "cm"),
    legend.text = element_text(size = 6)
  )
```

